Evaluation of probabilistic photometric redshift estimation approaches for \boldblue{ \textsc{The Rubin Observatory Legacy Survey of Space and Time} (LSST)}

### 2020-04-04 paper/authors.tex
fixing affiliation

\author[LSST Dark Energy Science Collaboration]{
\parbox{\textwidth}{
\Large
S.J.~Schmidt$^{1}$,
A.I.~Malz$^{2,3,4}$,
J.Y.H.~Soo$^{5,6}$,
I.A.~Almosallam$^{7,8}$,
M.~Brescia$^{9}$,
S.~Cavuoti$^{9,10}$,
J.~Cohen-Tanugi$^{11}$,
A.J.~Connolly$^{12}$,
J.~DeRose$^{13,14,15,16,17}$,
P.E.~Freeman$^{18}$,
M.L.~Graham$^{12}$,
K.G.~Iyer$^{19,20}$,
M.J.~Jarvis$^{21,22}$,
J.B.~Kalmbach$^{12}$,
E.~Kovacs$^{23}$,
A.B.~Lee$^{18}$,
G.~Longo$^{10}$,
C.B.~Morrison$^{12}$,
J.A.~Newman$^{24}$,
E.~Nourbakhsh$^{1}$,
E.~Nuss$^{11}$,
T.~Pospisil$^{18}$,
H.~Tranin$^{11}$,
R.H.~Wechsler$^{25,16,26}$,
R.~Zhou$^{15,24}$,
R.~Izbicki$^{27,28}$
\begin{center} (LSST Dark Energy Science Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
%\scriptsize
$^{1}$ Department of Physics, University of California, One Shields Ave., Davis, CA, 95616, USA\\
$^{2}$ German Centre of Cosmological Lensing, Ruhr-Universitaet Bochum, Universitaetsstra{\ss}e 150, 44801 Bochum, Germany\\
$^{3}$ Center for Cosmology and Particle Physics, New York University, 726 Broadway, New York, 10003, USA\\
$^{4}$ Department of Physics, New York University, 726 Broadway, New York, 10003, USA\\
$^{5}$ School of Physics, University of Science Malaysia, 11800 USM, Pulau Pinang, Malaysia\\
$^{6}$ Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK\\
$^{7}$ King Abdulaziz City for Science and Technology, Riyadh 11442, Saudi Arabia\\
$^{8}$ Information Engineering, Parks Road, Oxford, OX1 3PJ, UK\\
$^{9}$ INAF-Astronomical Observatory of Capodimonte, Salita Moiariello 16, 80131 Napoli, Italy\\
$^{10}$ Department of Physics E. Pancini, University Federico II, via Cinthia 6, I-80126, Napoli, Italy\\
$^{11}$ Laboratoire Univers et Particules de Montpellier, Universit\'e de Montpellier, CNRS, Montpellier, France\\
$^{12}$ DIRAC Institute and Department of Astronomy, University of Washington, Box 351580, U.W., Seattle WA 98195, USA\\
$^{13}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
$^{14}$ Berkeley Center for Cosmological Physics, Department of Physics, University of California, Berkeley CA 94720\\
$^{15}$ Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA\\
$^{16}$ Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{17}$ Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Stanford, CA 94305, USA\\
$^{18}$ Department of Statistics \& Data Science, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA\\
$^{19}$ Dunlap Institute for Astronomy \& Astrophysics, University of Toronto, 50 St. George Street, Toronto, ON M5S 3H4, Canada\\
$^{20}$ Department of Physics and Astronomy, Rutgers, The State University of New Jersey, 136 Frelinghuysen Road, Piscataway, NJ 08854-8019 USA\\
$^{21}$ Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
$^{22}$ Department of Physics and Astronomy, University of the Western Cape, Bellville 7535, South Africa\\
$^{23}$ Argonne National Laboratory, Lemont, IL 60439, USA\\
$^{24}$ Department of Physics and Astronomy and the Pittsburgh Particle Physics, Astrophysics and Cosmology Center (PITT PACC), University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{25}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
$^{26}$ SLAC National Accelerator Laboratory, Menlo Park, CA, 94025, USA\\
$^{27}$ Department of Statistics, Federal University of Sao Carlos, Sao Carlos, Brazil\\
$^{28}$ External collaborator\\
}
}

>>>>

\author[LSST Dark Energy Science Collaboration]{
\parbox{\textwidth}{
\Large
S.J.~Schmidt$^{1}$,
A.I.~Malz$^{2,3,4}$,
J.Y.H.~Soo$^{5,6}$,
I.A.~Almosallam$^{7,8}$,
M.~Brescia$^{9}$,
S.~Cavuoti$^{9,10}$,
J.~Cohen-Tanugi$^{11}$,
A.J.~Connolly$^{12}$,
J.~DeRose$^{13,14,15,16,17}$,
P.E.~Freeman$^{18}$,
M.L.~Graham$^{12}$,
K.G.~Iyer$^{19,20}$,
M.J.~Jarvis$^{21,22}$,
J.B.~Kalmbach$^{12}$,
E.~Kovacs$^{23}$,
A.B.~Lee$^{18}$,
G.~Longo$^{10}$,
C.B.~Morrison$^{12}$,
J.A.~Newman$^{24}$,
E.~Nourbakhsh$^{1}$,
E.~Nuss$^{11}$,
T.~Pospisil$^{18}$,
H.~Tranin$^{11}$,
R.H.~Wechsler$^{25,16,26}$,
R.~Zhou$^{15,24}$,
R.~Izbicki$^{27,28}$
\begin{center} (LSST Dark Energy Science Collaboration) \end{center}
}
\vspace{0.4cm}
\\
\parbox{\textwidth}{
%\scriptsize
$^{1}$ Department of Physics, University of California, One Shields Ave., Davis, CA, 95616, USA\\
$^{2}$ Ruhr-University Bochum, Astronomical Institute, German Centre for Cosmological Lensing, Universitaetsstr. 150, 44801 Bochum, Germany\\
$^{3}$ Center for Cosmology and Particle Physics, New York University, 726 Broadway, New York, 10003, USA\\
$^{4}$ Department of Physics, New York University, 726 Broadway, New York, 10003, USA\\
$^{5}$ School of Physics, University of Science Malaysia, 11800 USM, Pulau Pinang, Malaysia\\
$^{6}$ Department of Physics and Astronomy, University College London, Gower Street, London WC1E 6BT, UK\\
$^{7}$ King Abdulaziz City for Science and Technology, Riyadh 11442, Saudi Arabia\\
$^{8}$ Information Engineering, Parks Road, Oxford, OX1 3PJ, UK\\
$^{9}$ INAF-Astronomical Observatory of Capodimonte, Salita Moiariello 16, 80131 Napoli, Italy\\
$^{10}$ Department of Physics E. Pancini, University Federico II, via Cinthia 6, I-80126, Napoli, Italy\\
$^{11}$ Laboratoire Univers et Particules de Montpellier, Universit\'e de Montpellier, CNRS, Montpellier, France\\
$^{12}$ DIRAC Institute and Department of Astronomy, University of Washington, Box 351580, U.W., Seattle WA 98195, USA\\
$^{13}$ Santa Cruz Institute for Particle Physics, Santa Cruz, CA 95064, USA\\
$^{14}$ Berkeley Center for Cosmological Physics, Department of Physics, University of California, Berkeley CA 94720\\
$^{15}$ Lawrence Berkeley National Laboratory, 1 Cyclotron Road, Berkeley, CA 94720, USA\\
$^{16}$ Kavli Institute for Particle Astrophysics and Cosmology and Department of Physics, Stanford University, Stanford, CA 94305, USA\\
$^{17}$ Department of Particle Physics and Astrophysics, SLAC National Accelerator Laboratory, Stanford, CA 94305, USA\\
$^{18}$ Department of Statistics \& Data Science, Carnegie Mellon University, 5000 Forbes Avenue, Pittsburgh, PA 15213, USA\\
$^{19}$ Dunlap Institute for Astronomy \& Astrophysics, University of Toronto, 50 St. George Street, Toronto, ON M5S 3H4, Canada\\
$^{20}$ Department of Physics and Astronomy, Rutgers, The State University of New Jersey, 136 Frelinghuysen Road, Piscataway, NJ 08854-8019 USA\\
$^{21}$ Astrophysics, Department of Physics, University of Oxford, Denys Wilkinson Building, Keble Road, Oxford, OX1 3RH, UK\\
$^{22}$ Department of Physics and Astronomy, University of the Western Cape, Bellville 7535, South Africa\\
$^{23}$ Argonne National Laboratory, Lemont, IL 60439, USA\\
$^{24}$ Department of Physics and Astronomy and the Pittsburgh Particle Physics, Astrophysics and Cosmology Center (PITT PACC), University of Pittsburgh, Pittsburgh, PA 15260, USA\\
$^{25}$ Department of Physics, Stanford University, 382 Via Pueblo Mall, Stanford, CA 94305, USA\\
$^{26}$ SLAC National Accelerator Laboratory, Menlo Park, CA, 94025, USA\\
$^{27}$ Department of Statistics, Federal University of Sao Carlos, Sao Carlos, Brazil\\
$^{28}$ External collaborator\\
}
}
